\section{Summary}
From the examples we have shown, one can make several observations
concerning the overall behavior of the algorithms and in which
situations certain algorithms would be preferred.

In any case, if there is a real concern for making sure the average regret
goes to 0 in the long run, and not merely some low, yet non-zero, value, then
none of the discretization algorithms should be used.  This is due simply to
the inherent bias in choosing a set of points to represent the entire domain.
In this case, the
$\mathcal{X}$-armed algorithm appears to be better than the Zooming algorithm.
In one dimension, this is due to the fact that the $\mathcal{X}$-armed
algorithm converges more quickly, at the expense of a higher computational
cost.  It may still be true in higher dimensions that the $\mathcal{X}$-armed
algorithm outperforms the Zooming algorithm, but due to the much larger amount
of time required to explore higher dimensions, combined with the computational
complexity of both algorithms, it is hard
to say for certain.  In high dimensions, though, it can be said for certain
that the Zooming algorithm is completely impractical due to the computational
cost of the covering oracle.

If we are not too concerned with actually achieving 0 average regret, but
rather only with achieving small average regret, the choice of algorithm is
less clear.  In higher dimensions, the Zooming algorithm will still take
infeasibly long to compute, and the $\mathcal{X}$-armed algorithm tends to
take a while to explore, so unless a large number of rounds are available,
a discretization algorithm is probably the best algorithm to use, with
the number of arms scaled according to how many rounds are available.

In one dimension, if very few rounds are allowed, then the $\epsilon$-greedy
with a small number of arms is likely to work best, as even in one dimension
the $\mathcal{X}$-armed algorithm takes \emph{some} time to explore.  If
we are allowed a larger number of rounds (on the order of 10,000 or so), the
$\mathcal{X}$-armed algorithm and the discretized $\epsilon$-greedy
algorithm, with a suitable number of arms, are the algorithms to choose.  With
a very large number of rounds available, the computational complexity of the
$\mathcal{X}$-armed algorithm makes it infeasible, and we can either go with
one of the discretization algorithms with a large number of arms or the
Zooming algorithm, for which average regret should go to 0 eventually.

Among the discretization algorithms, in all cases that we have been able to
test, the $\epsilon$-greedy algorithm converges swiftest.  By modifying
$\sigma$ and $\gamma$ in the UCB1 and Exp3 algorithms, though, we can speed up
convergence and make them perform nearly as well as the $\epsilon$-greedy
algorithm.